Comparison of Catalogs

### 2024-10-02 compare/compare.tex
replaced scatter plot

  \begin{itemize}
  \tightlist
  \item
    Similar to B-band completeness when measured with K\_s-band
    luminosity as a tracer for stellar mass. Overdensity at small
    distances and cut-off at large distances are observed.
  \end{itemize}
\item
  Completeness in terms of star formation rate (SFR):

  \begin{itemize}
  \item
    \textasciitilde50\% complete between 30 and 150 Mpc.
  \item
    Lower SFR completeness due to limitations in WISE-based SFR
    estimates, which lack full sky coverage.
  \item
    Despite IRAS's limited depth, it provides \textgreater50\% coverage
    for star-forming galaxies in the local neighborhood.
  \end{itemize}
\end{itemize}

@@

\begin{longtable}[]{@{}cccc@{}}
\toprule\noalign{}
LCV & HECATE & Description & Pearson Correlation {[}-1,1{]} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Ra\_1 & RA\_2 & Right Ascension & 1.0 \\
Dec\_1 & DEC\_2 & Declination & 1.0 \\
Dis & D & Distance & 0.881 \\
\end{longtable}

\subsubsection{Right Ascension}

\includegraphics{compare_files/figure-pdf/cell-13-output-1.pdf}

\subsubsection{Declination}

\includegraphics{compare_files/figure-pdf/cell-14-output-1.pdf}

\subsubsection{Distance}

@@

\includegraphics{compare_files/figure-pdf/cell-17-output-1.pdf}

\includegraphics{compare_files/figure-pdf/cell-19-output-1.pdf}

@@

\includegraphics{compare_files/figure-pdf/cell-22-output-1.pdf}

@@

\includegraphics{compare_files/figure-pdf/cell-23-output-1.pdf}

@@

\begin{minipage}{0.50\linewidth}
\includegraphics{compare_files/figure-pdf/cell-29-output-1.pdf}\end{minipage}%
%
\begin{minipage}{0.50\linewidth}
\includegraphics{compare_files/figure-pdf/cell-29-output-2.pdf}\end{minipage}%
\newline
\begin{minipage}{\linewidth}

@@

\includegraphics{compare_files/figure-pdf/cell-30-output-1.pdf}

@@

\includegraphics{compare_files/figure-pdf/cell-32-output-1.pdf}

@@

\includegraphics{compare_files/figure-pdf/cell-34-output-1.pdf}

@@

\subsubsection{B mag}

\subsubsection{K mag}

\includegraphics{compare_files/figure-pdf/cell-39-output-1.pdf}

@@

\includegraphics{compare_files/figure-pdf/cell-41-output-1.pdf}

{[}?{]}

@@

\includegraphics{compare_files/figure-pdf/cell-43-output-1.pdf}

@@

@@

\begin{longtable}[]{@{}ll@{}}
\toprule\noalign{}
& Percantage Change {[}\%{]} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
count & 64 \\
mean & -1 \\
std & 5 \\
min & -19 \\
50\% & 1 \\
max & 9 \\
\end{longtable}

\includegraphics{compare_files/figure-pdf/cell-48-output-1.pdf}

@@

>>>>

  \begin{itemize}
  \item
    Similar to B-band completeness when measured with \(K_s\)-band
    luminosity as a tracer for stellar mass.
  \item
    Overdensity at small distances and cut-off at large distances are
    observed.
  \end{itemize}
\item
  Completeness in terms of star formation rate (SFR):

  \begin{itemize}
  \item
    \textasciitilde50\% complete between 30 and 150 Mpc.
  \item
    Lower SFR completeness due to limitations in WISE-based SFR
    estimates, which lack full sky coverage.
  \item
    Despite IRAS's limited depth, it provides \textgreater50\% coverage
    for star-forming galaxies in the local neighborhood.
  \item
    HECATE's nonuniform SFR and stellar mass coverage, affecting the
    reliability of stellar population parameters.
  \end{itemize}
\end{itemize}

@@

\begin{longtable}[]{@{}cccc@{}}
\toprule\noalign{}
LCV & HECATE & Description & Pearson Correlation {[}-1,1{]} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Dis & D & Distance & 0.881 \\
\end{longtable}

\includegraphics{compare_files/figure-pdf/fig-coord-compare-output-1.pdf}

\caption{\label{fig-coord-compare}Comparison of the Distances}

\begin{itemize}
\tightlist
\item
  The average error of the distance in the HECATE catalog is
  \(\overline{E_D} = \pm 1.6\) Mpc, so the intercept is included in the
  error.
\item
  So we can assume that the Distances are the same
\end{itemize}

@@

\includegraphics{compare_files/figure-pdf/fig-vel-compare-output-1.pdf}

\caption{\label{fig-vel-compare}Comparison of the Radial Velocities}

\begin{itemize}
\tightlist
\item
  The average error of the radial velocity in the HECATE catalog is
  \(\overline{E_V} = \pm 12\text{km}\cdot s^{-1}\) , so the intercept is
  included in the error.
\item
  So we can assume that the radial velocities are the same
\end{itemize}

@@

\includegraphics{compare_files/figure-pdf/fig-types-compare-output-1.pdf}

\subcaption{\label{fig-types-compare-1}All the galaxies, without the
correction}

\includegraphics{compare_files/figure-pdf/fig-types-compare-output-2.pdf}

\subcaption{\label{fig-types-compare-2}Comparison with the correction
\(|{T_{HECATE}-T_{LCV}}|<7\)}

\caption{\label{fig-types-compare}Comparison of the Types of galaxies}

@@

\begin{itemize}
\tightlist
\item
  The average uncertainty of the morphological type in the HECATE
  catalog is \(\overline{E_T} = \pm 1.4\), so the intercept is included
  in the error.
\item
  So we can assume that the Distances are the same
\end{itemize}

@@

\begin{minipage}{0.50\linewidth}
\includegraphics{compare_files/figure-pdf/cell-24-output-1.pdf}\end{minipage}%
%
\begin{minipage}{0.50\linewidth}
\includegraphics{compare_files/figure-pdf/cell-24-output-2.pdf}\end{minipage}%

@@

\includegraphics{compare_files/figure-pdf/fig-axis-compare-output-1.pdf}

\subcaption{\label{fig-axis-compare-1}Linear scale}

\includegraphics{compare_files/figure-pdf/fig-axis-compare-output-2.pdf}

\subcaption{\label{fig-axis-compare-2}\(log_{10}\) scale}

\caption{\label{fig-axis-compare}Comparison of the Major Axises of the
galaxies}

@@

\(\overline{R_1} = 3.9\) {[}arcmin{]}, \(\overline{a_{26}} = 9.3\)
{[}arcmin{]}, so the intercept is negligable. \[
R_1 = 0.48\cdot a_{26}-0.34 \sim \frac{1}{2}a_{26}
\]

\[
\log(R1) = 0.89\log(a_{26})-10^{0.38} = \log(10^{-0.38}a_{26}^{0.89}) = \log(0.41\cdot a_{26}^{0.89})\Rightarrow R1\simeq \frac{a_{26}}{2}
\]

@@

\includegraphics{compare_files/figure-pdf/fig-klum-compare-output-1.pdf}

\caption{\label{fig-klum-compare}Comparison of the \(L_K\) of the
galaxies}

\[
\log(L_{K,HEC})=1.16\log(L_{K,LCV})-1.78=\log\left(\frac{{L_{K,LCV}}^{1.16}}{10^{1.78}}\right) \Leftrightarrow L_{K,HEC}=0.02\cdot{L_{K,LCV}}^{1.16}
\]

So as we can see the usage of a linear fitting is not correct here. But
we can clearly see a linear correlation.

We will use the relative difference of the two luminosities, to see if
statistically they are the same:

\includegraphics{compare_files/figure-pdf/cell-29-output-1.pdf}

@@

\includegraphics{compare_files/figure-pdf/fig-mag-compare-output-1.pdf}

\subcaption{\label{fig-mag-compare-1}\(M_B\)}

\includegraphics{compare_files/figure-pdf/fig-mag-compare-output-2.pdf}

\subcaption{\label{fig-mag-compare-2}\(M_K\)}

\caption{\label{fig-mag-compare}Comparison of the Magnitudes of the
galaxies}

\begin{itemize}
\tightlist
\item
  \(M_B\): it is a 1-1 correlation, since the average error
  \(M_{B,HECATE} = 0.4\ mag\), so the itercept is smaller than the error
\item
  \(M_K\): we need to examine it more, since the intercept is bigger
  than the error \(M_{K,HECATE} = 0.09\ mag\)
\end{itemize}

\includegraphics{compare_files/figure-pdf/cell-35-output-1.pdf}

\includegraphics{compare_files/figure-pdf/cell-35-output-2.pdf}

@@

{[}?{]} this 5\% average in the difference probably exists because of
the low number of galaxies we compare, so we can ignore it.

@@

\includegraphics{compare_files/figure-pdf/fig-sfr-lcv-output-1.pdf}

\subcaption{\label{fig-sfr-lcv-1}Linear scale}

\includegraphics{compare_files/figure-pdf/fig-sfr-lcv-output-2.pdf}

\subcaption{\label{fig-sfr-lcv-2}Decimal logarithmic scale}

\caption{\label{fig-sfr-lcv}Comparison of the \$SFR\_\{FUV\}-SFR\_\{Ha\}
of the galaxies}

The SFR according to Kroupa et al. (2020), can be calculated from the
mean of SFR from the Ha and FUV, for \(SFR>10^{-3}\ M_\odot\, yr^{-1}\).
As we can see from the plots Figure~\ref{fig-sfr-lcv} it is a good
aproximation for all SFR's

\[
SFR = \frac{SFR_{FUV}+SFR_{H\alpha}}{2}, \text{if both exist, else: } SFR = SFR_i,\ i= FUV,\, H\alpha
\]

\includegraphics{compare_files/figure-pdf/fig-sfr-compare-output-1.pdf}

\subcaption{\label{fig-sfr-compare-1}Linear scale}

\includegraphics{compare_files/figure-pdf/fig-sfr-compare-output-2.pdf}

\subcaption{\label{fig-sfr-compare-2}Decimal logarithmic scale}

\caption{\label{fig-sfr-compare}Comparison of the SFR's of the galaxies}

?EXPLANATION? this low correlation maybe comes from the
inaccuracy/approximation of Kroupa et al. (2020)

@@

\includegraphics{compare_files/figure-pdf/fig-mass-compare-output-1.pdf}

\caption{\label{fig-mass-compare}Comparison of the Stellar Masses of the
galaxies}

\includegraphics{compare_files/figure-pdf/cell-44-output-1.pdf}

\[
\log{M_{*,HECATE}}=1.07\cdot\log{M_{*,LCV}}-0.69, \text{ but } \log{M_*}>6\Rightarrow M_{*,HEC}\sim M_{*,LCV}
\]

As we can see the aproximation of Mass/Light=const.=0.6 is a pretty good
approximation, for the calculation of \(\log(M_*/M_\odot)\), especially
for high-mass galaxies

@@

@@

\bibitem[\citeproctext]{ref-kroupaConstraintsStarFormation2020}
Kroupa, P, M Haslbauer, I Banik, S T Nagesh, and J Pflamm-Altenburg.
2020. {``Constraints on the Star Formation Histories of Galaxies in the
{Local Cosmological Volume}.''} \emph{Monthly Notices of the Royal
Astronomical Society} 497 (1): 37--43.
\url{https://doi.org/10.1093/mnras/staa1851}.
